The prevalence of child welfare system contact among American Indian / Alaska Native children, 2003 - 2016

### 2020-05-18 ms.rmd
update data

```{r include=F}
rm(list=ls()); gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
library(lubridate)
library(gridExtra)
source("lifetable.r")
theme_set(theme_bw())

ncands_inv<-read_csv("./data/ncands_first_inv.csv") %>% 
  filter(year>=2003, year<2017) %>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
ncands_sub<-read_csv("./data/ncands_first_sub.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_fc<-read_csv("./data/afcars_first_fc.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>%   
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_tpr<-read_csv("./data/afcars_tpr.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White") 
afcars_non_icwa<-read_csv("./data/afcars_non_icwa.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_fc_inv<-read_csv("./data/afcars_fc_post_inv.csv")%>% 
  filter(year>=2003, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
```

@@

grid.arrange(ts, age)
```

@@

grid.arrange(ts, age)

@@

ggplot(ncands_sub_inv,
         aes(x = age, y = sub_inv, color = race_ethn)) +
  geom_line() + 
  geom_point() + 
  xlab("Age") + 
  ylab("Risk of event")
```

@@

grid.arrange(ts, age)

@@

ggplot(fc_cond_inv,
       aes(x = age, y = fc_inv, 
           color = race_ethn)) + 
  geom_line()
```

@@

grid.arrange(ts, age)
```

>>>>

```{r include=F}
rm(list=ls()); gc()
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(tidyverse)
library(lubridate)
library(gridExtra)
library(bookdown)
source("lifetable.r")
theme_set(theme_bw())

ncands_inv<-read_csv("./data/ncands_first_inv.csv") %>% 
  filter(year>=2011, year<2017) %>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
ncands_sub<-read_csv("./data/ncands_first_sub.csv")%>% 
  filter(year>=2011, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_fc<-read_csv("./data/afcars_first_fc.csv")%>% 
  filter(year>=2011, year<2017)%>% 
  filter(age<18) %>%   
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_tpr<-read_csv("./data/afcars_tpr.csv")%>% 
  filter(year>=2011, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White") 
afcars_non_icwa<-read_csv("./data/afcars_non_icwa.csv")%>% 
  filter(year>=2011, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
afcars_fc_inv<-read_csv("./data/afcars_fc_post_inv.csv")%>% 
  filter(year>=2011, year<2017)%>% 
  filter(age<18) %>% 
  filter(.imp!=0) %>% 
  filter(race_ethn == "AI/AN" | race_ethn == "White")
```

@@

grid.arrange(ts, age)
p_out<-arrangeGrob(ts, age)
ggsave("./vis/aian_inv.pdf", p_out)
```

@@

grid.arrange(ts, age)
p_out<-arrangeGrob(ts, age)
ggsave("./vis/aian_sub.pdf", p_out)
```

@@

p<-ggplot(ncands_sub_inv,
         aes(x = age, y = sub_inv, color = race_ethn)) +
  geom_line() + 
  geom_point() + 
  xlab("Age") + 
  ylab("Risk of event")

p

ggsave("./vis/aian_sub_inv.pdf", p)
```

@@

grid.arrange(ts, age)
p_out<-arrangeGrob(ts, age)
ggsave("./vis/aian_fc.pdf", p_out)
```

@@

# ggplot(fc_cond_inv,
#        aes(x = age, y = fc_inv, 
#            color = race_ethn)) + 
#   geom_line()
```

@@

grid.arrange(ts, age)
p_out<-arrangeGrob(ts, age)
ggsave("./vis/aian_icwa.pdf", p_out)
```
